---
title: "R introduction"
author: "H24061210"
date: "2019/5/14—¥"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Getting started to R 
## Simple calculation

* We can type simple arithmetical expressions:
```{r}
5 + 49
3 - 8
12 / 4
```

If you want to quit your R session when it is running, type:

`q()`

* Some other calculation with R
```{r}
3^4
31 %% 7
```
>Which mean the remainder after division of 31 by 7

```{r}
31 %/% 7
```
>And the integer part of a fraction

```{r}
7 * 4^2 + 3
```
>$$7 * 4^2 + 3$$

##Logical vectors
We have used the `c()` function to put numeric vectors together as well
as character vectors.\
\*Some examples¡G\*
```{r}
c(1,2,2,3,3,3)
```
```{r}
a=c(TRUE,FALSE,FALSE,TRUE,FALSE)
sum(a)
```
>Because \"TRUE\" implies 1,\"FALSE\" implies 0.

##Data input and output
1. To work with data in the folder **mydata** on the **C: drive**, type `setwd("c:/mydata")` or `setwd("c:\\ mydata")`
2. To save object you heve **constructed** for a future session, type\
`dump("usefuldata", "useful.R")`

##Programming statistical graphics
1. Barchart: `barplot()`\
  for example:
```{r}
x=c(1,2,3,4)
barplot(x)
```
2. pie chart: `pie()`\
  for example:
```{r}
groupsizes <- c(18, 30, 32, 10, 10)
labels <- c("A", "B", "C", "D", "F")
pie(groupsizes, labels, col=c("grey40", "white", "grey", "black", "grey90"))
```
3. Histograms:`hist()`
  for example:
```{r}
x <- rnorm(100)
hist(x)
```
4. QQ plots:`qqplot()`
  for example:
```{r}
X <- rnorm(1000)
A <- rnorm(1000)
qqplot(X, A, main="A and X are the same")
```

>The line is almost straight.

###Adding to plots
We can just simply type `plot()` and get a graphic, what else can we do?\
*points(x, y, ...)*\
*lines(x, y, ...) adds line segments*\
*text(x, y, labels, ...) adds text into the graph*\
*abline(a, b, ...) adds the line y = a + bx*\
*abline(h=y, ...) adds a horizontal line*\
*abline(v=x, ...) adds a vertical line*\
*polygon(x, y, ...) adds a closed and possibly filled polygon*\
*segments(x0, y0, x1, y1, ...) draws line segments*\
*arrows(x0, y0, x1, y1, ...) draws arrows*\
*symbols(x, y, ...) draws circles, squares, thermometers, etc.*\
*legend(x, y, legend, ...) draws a legend.*

####Also, there is another way to plot a function by using `curve()`.

#Programming with R
##Flow control
###1. The *for()* loop
* The for() statement allows one to specify that a **certain operation**
should be **repeated** a fixed number of times.\
* Syntax¡G
`for (name in vector) {commands}`\
  forexample:\
The Fibonacci sequence is a famous sequence in mathematics.

```{r}
Fibonacci <- numeric(12)
Fibonacci[1] <- Fibonacci[2] <- 1
for (i in 3:12) Fibonacci[i] <- Fibonacci[i - 2] + Fibonacci[i - 1]
Fibonacci
```
Or we can use for loop to calculate more complex math questuion.
```{r}
i <- 0.006
for (j in 1:1000) {
  i<-(1-(1+i)^(-20))/19
}
i
```

###2. The *if()* statement
* The if() statement allows us to control **which**
statements are executed.
* Syntax¡G\
`if (condition) {commands when TRUE}`\
`if (condition) {commands when TRUE} else {commands when FALSE}`\

* To avoid ambiguities such as this, a common convention for typing
if ... else is¡G\
```{r,eval=FALSE}
if (condition) {
  commands when TRUE
} else {
  commands when FALSE
}
```
###3. The *while()* loop
* The while() statement accomplishes **repeat** statements
* Syntax¡G\
`while (condition) {statements}`
+ The condition is evaluated, and if it evaluates to FALSE, nothing more
is done.

###4. The *repeat* loop, and the *break*
* Syntax : 
`repeat { statements }`\
This causes the statements to be **repeated endlessly**.
* Syntax :
`if (condition) break`
+ The **break** statement causes the loop to *terminate immediately*. **break**
statements can also be used in **for()** and **while()** loops.

##Define a function with R
* Functions are self-contained units with a well-defined purpose.In general,
functions take **inputs**, *do calculations* (possibly *printing intermediate
results*, *drawing graphs*, *calling other functions,* etc.), and produce **outputs**.
+ For example¡G
```{r}
annuityAmt <- function(n, R, i) {
  R*((1+i)^n-1)/i
}
annuityAmt(10, 400, 0.05)
```

>Use function() to calculate the output number with given input.$$R*((1+i)^n-1)/i$$

## Computational linear algebra
$$3*1-4x2=6\\
x1+2*2=-3$$

>####Q:How to solve this problem quickly?
 ####A:Construct a matrix.
 
###Constructing matrix objects
* Syntax¡G\
`matrix(data, nrow, ncol) ` `# data is a vector of nrow*ncol values`\
`cbind(d1, d2, ..., dm) ` `# d1, ..., dm are vectors (columns)`\
`rbind(d1, d2, ..., dn) ` `# d1, ..., dn are vectors (rows)`

```{r}
A=matrix(c(1,2,3,2,3,4,3,4,5),ncol = 3)
A
```

> Now we have a matrix!

+ And we can give the columns and rows names.
```{r}
colnames(A)<-c('x1','x2','x3')
rownames(A)<-c('y1','y2','y3')
A
```

###Matrix properties
* The dimension of a matrix is its number of **rows** and its number of **columns**.
```{r}
dim(A)
```

+ The diagonal elements can be obtained using the diag()function.
```{r}
diag(A)
```

+ The t() function is used to calculate the matrix transpose X^T.
```{r}
t(A)
```

###Solving linear systems
* The function solve(A, b)gives the solution to systems of equations of
the form Ax = b.
```{r,eval=FALSE}
b=c(1,2,1)
solve(A,b)
```

###Eigenvalues and eigenvectors
* Eigenvalues and eigenvectors can be computed using the function
eigen().
```{r}
eigen(A)
```

##Simulation
A operation is used internally by R to produce **pseudorandom
numbers** automatically with the function `runif()`.
```{r}
runif(20,max = 1,min = 0)
```

###Binomial random variables
* Syntax¡G\
1. `dbinom(x, size, prob)`

>Here, *size* and *prob* are the **binomial parameters** *m* and *p*, respectively,
while x denotes the number of **¡§successes.¡¨** The output from this function
is the value of **P(X = x)**.

2. `pbinom(n, size, prob)`

>The output from this function is the value of **P(X <= x)**.

3.`qbinom()`
>This function gives the **quantiles** for the binomial distribution.

###Poisson random variables
* Syntax¡G\
`dpois(x, lambda)`

>These probabilities can be evaluated using the `dpois()`function.

###Exponential random numbers
* Syntax¡G`pexp(q, rate)`
$$P(T<=t)=1-e^£ft$$

>The `pexp()` function can be used to evaluate thisfunction.

###Normal random variables
* Syntax¡G`rnorm(n, mean, sd)`

>This produces n **normal pseudorandom** variates which have mean *mean*
and standard deviation *sd*.

$$f(x)=1/(£m*¡Ô2£k)*e^(-((x-£g)^2/(2£m^2)))$$